Applications of the Fresnel Integrals

### 2019-03-16 draft.tex
application start

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.5\textwidth]{Fresnel-Integrals-(Normalised).png}
	\caption{Fresnel integrals \cite{wiki}.}
\end{figure}

@@

\section{Applications of Fresnel Integral}
The error functions, Fresnel integrals, and related functions occur in a variety of physical applications. Fresnel integrals and Cornu’s spiral occurred originally in the analysis of the diffraction of light; see Born and Wolf (1999, §8.7). More recently, Cornu’s spiral appears in the design of highways and railroad tracks, robot trajectory planning, and computer-aided design; see Meek and Walton (1992).

In optics, the illumination intensity at a point behind a slit is computed from the distance between two points on the Euler spi- ral. The Euler spiral also provides optimal curva- ture for train tracks between a straight run and an upcoming bend. It is striking that it can be also obtained with an orange and a kitchen knife.

The Euler spiral has applications in many fields of science.

The Euler spiral has applications in
many fields of science. In optics, the illumination
intensity at a point behind a slit is computed from
the distance between two points on the Euler spiral. The Euler spiral also provides optimal curvature for train tracks between a straight run and
an upcoming bend.

Fraunhofer diffraction, asymptotics of Weyl sums, and railway and freeway constructions.

\subsection{Application using the Euler Spiral}
\cite{BH12}
Electromagnetic field intensity
 in the physics of diffraction and is used in the theory of driving motorcar round a corner quickly.

\subsection{Further Applications}

>>>>

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.4\textwidth]{Fresnel-Integrals-(Normalised).png}
	\caption{Fresnel integrals \cite{wiki}.}
\end{figure}

@@

\section{Applications of the Fresnel Integrals}
Fresnel Integrals and Euler spiral have applications in many fields of science. They occurred originally in the analysis of the diffraction of light. More recently, Euler spiral appears in the design of highways and railroad tracks, robot trajectory planning, and computer-aided design. In this section, we will describe two main applications of the Fresnel integrals in detail, namely the original Fresnel Diffraction and the railway construction.

\subsection{Fresnel Diffraction}
\cite{BH12}
Electromagnetic field intensity
in the physics of diffraction

In optics, the illuminationintensity at a point behind a slit is computed from the distance between two points on the Euler spiral.

\subsection{Railway  Construction}

 is used in the theory of driving motorcar round a corner quickly.

 The Euler spiral also provides optimal curvature for train tracks between a straight run and an upcoming bend.
